I am excited to apply for the Software Engineer position at your esteemed organization. My academic background in Electronics and Communication, coupled with my practical experience in software development, makes me a strong candidate for this role.

Currently, as an \textbf{AI (R\&D)} Intern at Brainlox.ai, I am part of the MVP team working on creating \textbf{back-end APIs} using AWS Lambda and API Gateway. I have played a crucial role in researching and implementing the featured AI tutor product, leading to a \textbf{70\%} increase in \textbf{customer retention rate}. I also have experience with \textbf{sentiment analysis}, which is vital in understanding and enhancing user experiences.

Before Brainlox.ai, I interned as a \textbf{Software Engineer} at Localytee. I worked on front-end development, creating a landing page using \textbf{React.js} for a US-based real estate client, and fixed issues on a \textbf{React Native mobile app}. These experiences have honed my skills in developing \textbf{scalable and robust software solutions}.

My project experience is vast, ranging from developing a web-based application for colleges to track and search their alumni, creating a dog breed predictor app utilizing \textbf{machine learning} technologies, to developing a conversational \textbf{AI bot using Python} and the OpenAI API.

Proficient in \textbf{Machine Learning, Python, JavaScript,} \textbf{MERN STACK} CSS, and HTML, with intermediate skills SQL, I have a deep understanding of \textbf{software development principles}. I have experience with various libraries and frameworks such as \textbf{jQuery, Node.js, and React.js}. In addition, I have used tools like \textbf{Git, Jupyter, Collab, and VS Code} extensively in my projects.

As the \textbf{head} of the \textbf{AI Circle at The Machine Learning Club} of SMVDU and an organizer for the \textbf{SMVDU Tech Community}, I have developed \textbf{strong leadership and team collaboration skills}. These roles have taught me how to effectively work in a team and lead projects to successful completion.

In conclusion, I am excited about the opportunity to bring my unique blend of skills and experience to your team and contribute to your software development efforts. I appreciate your time and consideration and look forward to the possibility of discussing my application further.
